Simulations

### 2018-04-18 check-cmsa.Rmd
save

```{r}
library(bigsnpr)
celiac2 <- snp_attach("backingfiles/celiacQC_sub1.rds")
CHR <- celiac2$map$chromosome
POS <- celiac2$map$physical.pos
(G <- celiac2$genotypes)
(G2 <- big_attach("backingfiles/celiacQC_sub1_tripled1.rds"))

covar.all <- readRDS("backingfiles/PCA2.rds")$u

n <- nrow(G)
ind.HLA <- snp_indLRLDR(CHR, POS, subset(LD.wiki34, ID == "hild12"))
```

@@

### Scenario n°1 (with T-Trees)

```{r}
params.grid1 <- expand.grid(
  n.train    = 6000,
  par.causal = list(c(30, "all"), c(300, "all"), c(3000, "all"), c(30, "HLA")), 
  par.dist   = c("gaussian", "laplace"), 
  par.h2     = 0.8, 
  par.model  = c("simple", "fancy"),
  num.simu   = 1:5,
  stringsAsFactors = FALSE
) 
```

```{r, eval=TRUE}
if (!dir.exists("results1")) dir.create("results1")

for (i in rows_along(params.grid1)) {

  res.file <- paste0("results1/simu_", i, ".rds")
  if (file.exists(res.file)) next

  params <- params.grid1[i, ]
  par.causal <- params[["par.causal"]][[1]]

  # Get results from all methods
  res <- bind_rows(
    PRS(G, CHR, POS, pheno.all, covar.all, ind.train, ind.test),
    logit.CMSA(G,  pheno.all, covar.all, ind.train, ind.test, "logit-simple"),
    logit.CMSA(G2, pheno.all, covar.all, ind.train, ind.test, "logit-triple"),
    ttrees(TTree, "backingfiles/ttrees", pheno.all, ind.train, ind.test, n.trees = 100)
  )
  params[["res"]] <- list(res)
  saveRDS(unnest(params, res, .drop = FALSE), file = res.file)
}
```

>>>>

```{r}
library(bigsnpr)
celiac2 <- snp_attach("backingfiles/celiacQC.rds")
CHR <- celiac2$map$chromosome
POS <- celiac2$map$physical.pos
G <- celiac2$genotypes

covar.all <- readRDS("backingfiles/PCA.rds")$u

n <- nrow(G)
```

@@
